Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-08-12 docs/00-manuscripts/ieee/ieee-manuscript.tex
simplify
Update docs/00-manuscripts/ieee/ieee-manuscript.tex

% Ensuring a fair weighting in the ensemble
% JM: reading further on, it might be that there are only three classes, please refine, Patrick!
Filter methods can be grouped into four classes: Correlation-based, entropy-based, linear and non-linear methods.
Care needs to be taken to not weigh certain classes more than others in the ensemble as otherwise the final ranking result will be biased.
In this study this was taken care of by checking the rank correlations (Spearman's correlation) of the generated feature rankings of all methods against each other.
If filter pairs showed a correlation of 0.9 or higher, only one of the two was included into the ensemble filter, selected at random.
This ensured that the ensemble filter composition was not biased towards a certain group of filter methods.

>>>>

% Ensuring a fair weighting in the ensemble
% JM: reading further on, it might be that there are only three classes, please refine, Patrick!
Filter methods can be grouped into groups which are formed out of three binary classes: multivariate or univariate feature use, correlation or entropy-based importance weighting and linear and non-linear filter methodology.
Care needs to be taken to not weigh certain classes more than others in the ensemble as otherwise the final ranking result will be biased.
In this study this was taken care of by checking the rank correlations (Spearman's correlation) of the generated feature rankings of all methods against each other.
If filter pairs showed a correlation of 0.9 or higher, only one of the two was included into the ensemble filter, selected at random.
This ensured that the ensemble filter composition was not biased towards a certain group of filter methods.
